### 2016-10-29 doc/chap-3-refman.tex
Made the console debugger take names for printing CFGs and HTMLs

\section{\safe commands}
One can run a \safe command as follows:
\begin{verbatim}
safe {command} [-{option}]*
     [-{phase}:{option}[={input}]]* {filename}+
\end{verbatim}
For example, the following command analyzes JavaScript code stored in a file name
``{sample.js}'' located in the current directory without showing detailed information
from the \verb!astRewriter! phase but printing the result of the \verb!cfgBuilder!
phase into a file name ``{out}'':
\begin{verbatim}
safe analyze -astRewriter:silent
             -cfgBuilder:out=out sample.js
\end{verbatim}

@@

\safe writes the result of the phase to a file \verb!out!.
% \item[\doption{-{phase}:out={out}}]: \\
%   \safe writes the result of the phase to a file name \verb!out!.
\end{itemize}

@@

\medskip\noindent
\fbox{\texttt{print cfg}}\\[.2em]
It prints the current CFG to files \verb!cfg.gv! and \verb!cfg.pdf!.

\medskip\noindent
\fbox{\texttt{print html}}\\[.2em]
It prints the current CFG and its state to the \verb!cfg.html! file.
We describe this facility in the next section.

>>>>

\section{\safe commands}
One can run a \safe command as follows:
\begin{verbatim}
safe {command} [-{option}]*
     [-{phase}:{option}[={input}]]* {filename}+
\end{verbatim}
For example, the following command analyzes JavaScript code stored in a file name
``{sample.js}'' located in the current directory without showing detailed information
from the \verb!astRewriter! phase but printing the result of the \verb!cfgBuilder!
phase into a file name ``{out}'':
\begin{verbatim}
safe analyze -silent
             -cfgBuilder:out=out sample.js
\end{verbatim}

@@

\safe writes the result of the phase to a file \verb!out!.
% \item[\doption{-{phase}:out={out}}]: \\
%   \safe writes the result of the phase to a file name \verb!out!.
\end{itemize}
and the global options are \verb!-silent! and \verb!-testMode!.

@@

\medskip\noindent
\fbox{\texttt{print cfg \{name\}}}\\[.2em]
It prints the current CFG to files \verb!name.gv! and \verb!name.pdf!.

\medskip\noindent
\fbox{\texttt{print html \{name\}}}\\[.2em]
It prints the current CFG and its state to the \verb!name.html! file.
We describe this facility in the next section.
